Minimizing Time Required For Graduation

### 2010-12-11 paper/paper.tex

\section{Problem Description} To make our examples concrete we will focus on the
classes offered within the Math department; however, our algorithm and model can
be extended to include other departments.

@@

\subsection{Definitions} We will now formalize some terms used in our paper.
\begin{itemize} \item A {\it course} refers to any course offered by the
University of Washington. A course is identified by its department name and
number, for example {\it MATH309}. Each course is also worth a specific amount
of credits. \item We refer to a specific instance of a course as a {\it course
offering}. Additionally, each course offering  has associated with it the time of
the day at which the course meets, the quarter it is being offered, and the
section number of the offering. Throughout this paper, we will refer to quarters
by their time schedule abbreviates: {\it F} for Fall Quarter, {\it W} for Winter
Quarter, {\it Sp} for Spring Quarter, and {\it S} for Summer Quarter.
\end{itemize}

>>>>

\section{Problem Description} \label{psdesc} To make our examples concrete we will focus on the
classes offered within the Math department; however, our algorithm and model can
be extended to include other departments.

@@

\section{Model Elements} The solve the problem outlined in section \ref{pdesc}
we formalized elements of the academic quarter. Some of the hardest elements to
model were representing prerequisites for a course, how to handle quiz sections,
and simply choosing appropriate sets to contain information about a student's
academic progress.

\subsection{Classes and Quiz Sections} Another modeling difficulty that we
initially ignore was how to represent quiz sections for a class. Each time
a course is offered is may be offered as multiple classes. For instance, during
$F$ $MATH307$ is offered as 7 different sections all teaching the same material
during different time periods. Within a specific quarter schedule line number,
SLNs uniquely identify courses allowing us to differentiate between classes with
the same name. Continuing the above example, the SLNs of the 7 $MATH307$
instances may be 15432, 15433, 15434...

Our peer review team commented that we had not accounted for courses that
required concurrent quiz sections. First we note that the quiz sections for
a class never occur during the same time periods as the class itself (otherwise
students would not be able to attend the quiz section). Quiz sections also have
unique SLNs, to include a required quiz section we include the quiz section SLN
with the SLN for the associated class. Finally, courses such at $MATH125$ can
have multiple sections, each with several quiz sections of which only one need
be taken. We found the easiest way to represent this situation was to iterate
over the quiz sections for each class section and generate a puesdo class for
each pair of class section and quiz section that occured during the time periods
for both quiz and main sections. Fig. \ref{quizzes} contains one section
$MATH125$ being split across 3 quiz sections.
\begin{figure} [ht] 
    \begin{center}
        \includegraphics[scale=0.4]{quiz_sections} 
    \end{center}
    \caption{Splitting up MATH125} 
    \label{quizzes} 
\end{figure}

\subsection{Definitions} We will now formalize some terms used in our paper.
\begin{itemize} \item A {\it course} refers to any course offered by the
University of Washington. A course is identified by its department name and
number, for example {\it MATH309}. Each course is also worth a specific amount
of credits. \item We refer to a specific instance of a course as a {\it class}.
Each class has associated with it the time of the day at which it meets, the
quarter it is being offered, and the section number of the offering.  Throughout
this paper, we will refer to quarters by their time schedule abbreviates: {\it
F} for Fall Quarter, {\it W} for Winter Quarter, {\it Sp} for Spring Quarter,
and {\it S} for Summer Quarter. \end{itemize}
